Direction-Free In-Air Signature Verification Using WIFI CSI Signal

### 2019-05-16 190410_Paper_ACPR/paper_v1.tex
paper_acpr: v2 upload

\subsection{Contribution}
- Overcome cons of WIFI signature system
- Robust to signal direction, size

@@

\subsection{WIFI CSI}
- An In-Air Signature Verification System Using Wi-Fi Signals

@@

% description of siamese net
In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
% differences in feature extractor
They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector. Apart from this work based on ConvNet as feature extractor and L1 distance as feature matcher.
In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
% advantages of using Convnet filter
Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.

@@

\section{Experiments}

@@

>>>>

\subsection{Contribution}
- Overcome cons of WIFI signature systems
- Robust to signal direction, size

@@

\subsection{ConvNets}
% description of convnet
Convolutional Neural Networks is a specal case of MLP and it has unified feature extractor and classifier in one network. It has been widely applied to visual objects such as image or video or 2D array input. Several factors make ConvNets attractive in image related tasks.
Local connectivity captures local correlation property of image. It is applycable by using ConvNet filter.
Weight sharing helps to reduce the number of weights in feature maps.
Also, CUDA libraries makes the tranining feature maps easier to reduce training time.
%

@@

% description of siamese net
In \cite{bromley1994signature}, LeCun et al. Introduced Siamese nets as parts of their handwritten signature verification system. 
A siamese neural network consists of twin networks which accept distinct inputs but are joined by an energy function at the top.\cite{koch2015siamese}
% differences in feature extractor
They proposed a feature extractor based on Time Delay Neural Networks\cite{lang1990time} and feature matcher based on cosine distance of feature vector.

@@

\section{Experiments}
% Dataset
\subsubsection{Dataset}
 To evaluate validation performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used.
 % description
 we utilized 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) which is dimension of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas).

% network shape

% network parameters

@@

% old parts

% description of siamese
In this paper, we propose a for signature verification system that is applicable for WIFI CSI signal, which is more complex and larger than handwritten images. 
% advantages of using Convnet filter
Based on Convnets as feature extractor, we are able to make feature vector from CSI signal reflecting local connectivity between signals at a near frequency range and closer measurement time. 
The proposed method achieved better performance because it is applicable to all points of CSI signals. This is due to the weight sharing the property of the Convnet filter.
